---
title: "eds212-day5a-interactive"
format: html
execute: 
  warning: false
editor options:
  chunk_output_type: false
---
```{r}
#| warning: false
#| 

# load libraries
library(tidyverse)

```

Try using 'head()', 'tail()', and 'dim()'


```{r}
#| include: false 
# the code chunk can be omittted with the hash pipe above, these are called execution options ----  
# do some data exploration on the starwars df ----

head(starwars)
head(starwars, n= 50)

# the 'n' stands for amount of rows you want to see ----
tail(starwars)
dim(starwars)
dplyr::starwars

```


- Create a ggplot (scatterplot) of character mass (y-axis) and height (x-axis)
- update the color of the points so that color changes based on the value of mass

```{r}
#| warning: false
#| echo: false




ggplot(data = starwars, aes(x = height, y = mass, color = mass)) +
         geom_point() +
  labs(x = "Height (cm)", 
       y = "Mass (kg)", tittle = "here is my title")

# labs is = labels

# if you dont want to make color based on mass, you can set the color in  the geom_point layer

ggplot(data = starwars, aes(x = height, y = mass)) +
         geom_point(color = 'red')
```

- create a histogram of character heights 
- update the fill color to purple and the outside border line of each histogram bin to orange
- update axis labels
- update your code chuck options so that only your code and output graph appear in the rendered doc (no warninigs or messages)

```{r}

#| warning: false
ggplot(data = starwars, aes(y = height)) +
         geom_histogram(color = 'orange', fill = 'purple') +
  labs(x = 'character', y = 'height (cm)', title = 'idk' )

```

